Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-25 Web3D2013-Dec3D/paper.tex
Minor update: INRIA to Inria
Apparently, Inria is not an acronym anymore... ;)
removed vspace

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ INRIA \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sandynist@gmail.com} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI GmbH \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI GmbH \& Universit\"at des Saarlandes \\ Saarbr\"ucken \\ Germany
}

@@

\begin{figure}%[ht]
  \centering
  \includegraphics[width=1.0\columnwidth]{images/Declarative3d.png}
  \caption{The position of the Declarative 3D approach in the current Web graphics technology ecosystem.}
  \label{fig:DeclarativeVsImperative}
  \vspace{-0.2cm}
\end{figure}

@@

\begin{figure*}%[ht]
  \centering
  \includegraphics[width=1.0\textwidth]{images/ch_apps.png}
  \caption{From left to right: walktrough of Roman heritage site; cultural heritage object explorer with metadata; restored virtual synagoge.}
  \label{fig:chApps}
  \vspace{-0.2cm}
\end{figure*}

@@

\paragraph{Platform Independence}
3D content needs to be described in a way that does rely neither on a specific render API such as OpenGL or DirectX nor on a specific rendering technique such as rasterization or ray tracing only \cite{Rubinstein:2009,Schwenk12}. This should allow for content to be portable across browsers, rendering techniques, and hardware platforms, while taking advantage of available features wherever possible. The results of rendering content under such different environments should be highly predictable.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  \vspace{-0.2cm}
\end{figure}

\subsection{Evaluation platforms}
\label{subsection:evaluation}
With X3DOM \cite{Behr2009} and XML3D \cite{Sons2010} two evaluation platforms are available to support the ongoing discussion in the computer graphics and Web communities how an integration of HTML(5) and Declarative 3D content could look like.

@@

Both platforms are available under an Open Source license and used in many national and international research projects. From the user feedback and use-cases we were able to collect from the evaluation platforms, we were able to derive the essential features, that both approaches have in common and that we propose for a Dec3D standard.

% TODO: In the last paragraph of this section, we can write about the efforts to consolidate approaches and/or how the competing two frameworks influence one another for the common benefit...? This should be followed by the some link to the next section (polyfill).
\subsection{Declarative 3D Essentials}
\label{subsection:essentials}
In this section we briefly outline our proposed essential elements for an upcoming Dec3D standard. First of all, a start element allows the transition from the HTML flow layout to 3D transformations:

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\columnwidth]{images/Dec3D-Architecture.png}
  \caption{Proposed declarative 3D ``polyfill'' runtime architecture.}
  \label{fig:polyArch}
  \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.85\columnwidth]{images/polyfill.png}
  \caption{Levels of integration: current browser APIs only allow integrating with DOM and DOM Events, but not yet fully with CSS.}
  \label{fig:polyInt}
  \vspace{-0.2cm}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{images/cad_apps.png}
  \caption{From left to right: web-based design review application with annotation markers; interactive explosion of CAD model on iPad; lightweight web-based viewer for 3D CAD data; visualization and interactive exploration of simulation data by using extended mouse events.}
  \label{fig:cadApps}
  \vspace{-0.2cm}
\end{figure*}

>>>>

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ Inria \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sandynist@gmail.com} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI GmbH \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI GmbH \& Universit\"at des Saarlandes \\ Saarbr\"ucken \\ Germany
}

@@

\begin{figure}%[ht]
  \centering
  \includegraphics[width=1.0\columnwidth]{images/Declarative3d.png}
  \caption{The position of the Declarative 3D approach in the current Web graphics technology ecosystem.}
  \label{fig:DeclarativeVsImperative}
  %\vspace{-0.2cm}
\end{figure}

@@

\begin{figure*}%[ht]
  \centering
  \includegraphics[width=1.0\textwidth]{images/ch_apps.png}
  \caption{From left to right: walktrough of Roman heritage site; cultural heritage object explorer with metadata; restored virtual synagoge.}
  \label{fig:chApps}
  %\vspace{-0.2cm}
\end{figure*}

@@

\paragraph{Platform Independence}
3D content needs to be described in a way that does rely neither on a specific render API such as OpenGL or DirectX nor on a specific rendering technique such as rasterization or ray tracing only \cite{Rubinstein:2009,Schwenk12}. This should allow for content to be portable across web browsers, rendering techniques, and hardware platforms, while taking advantage of available features wherever possible. The results of rendering content under such different environments should be highly predictable.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  %\vspace{-0.2cm}
\end{figure}

\subsection{Evaluation platforms}
\label{subsection:evaluation}

With X3DOM \cite{Behr2009} and XML3D \cite{Sons2010} two evaluation platforms are available to support the ongoing discussion in the computer graphics and Web communities how an integration of HTML(5) and Declarative 3D content could look like.

@@

Both platforms are available under an Open Source license and used in many national and international research and industrial projects. From the user feedback and use cases we have collected from both evaluation platforms, we were able to derive the essential features, that both approaches have in common and that we propose for a Dec3D standard.

\subsection{Declarative 3D Essentials}
\label{subsection:essentials}

In this section we briefly outline our proposed essential elements for an upcoming Dec3D standard. First of all, a start element allows the transition from the HTML flow layout to 3D transformations:

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\columnwidth]{images/Dec3D-Architecture.png}
  \caption{Proposed declarative 3D ``polyfill'' runtime architecture.}
  \label{fig:polyArch}
  %\vspace{-0.2cm}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.85\columnwidth]{images/polyfill.png}
  \caption{Levels of integration: current browser APIs only allow integrating with DOM and DOM Events, but not yet fully with CSS.}
  \label{fig:polyInt}
  %\vspace{-0.2cm}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{images/cad_apps.png}
  \caption{From left to right: web-based design review application with annotation markers; interactive explosion of CAD model on iPad; lightweight web-based viewer for 3D CAD data; visualization and interactive exploration of simulation data by using extended mouse events.}
  \label{fig:cadApps}
  %\vspace{-0.2cm}
\end{figure*}
